### 2013-09-12 thesis/src/chapters/chapter-2.tex
Added comparision of providers' scaling capabilites

>>>>

\section{Providers comparision}

Table \ref{tab:cloud-providers-scaling} presents a summary of cloud provider scaling capabilites. Interestingly, all of them are focused solely on horizontal scaling, ignoring advantages offered by a fine-grained approach to scaling that leverage scaling up and application tuning.

\begin{table}[!htbp]
\begin{tabularx}{\textwidth}[]{ X  c  c  c }
\specialrule{.1em}{.05em}{.05em}

  & \textbf{Horizontal scaling} & \textbf{Vertical scaling} & \textbf{Application / resource tuning} \\
\specialrule{.1em}{.05em}{.05em}

\multicolumn{4}{ l }{\textbf{Infrastructure provider}} \\
\specialrule{.1em}{.05em}{.05em}

Carina & \checkmark & $\times$ & $\times$ \\ \hline

OneFlow & \checkmark & $\times$ & $\times$ \\ \hline

AWS EC2 & \checkmark & $\times$ & $\times$ \\ \hline

\multicolumn{4}{ l }{\textbf{Platform provider}} \\
\specialrule{.1em}{.05em}{.05em}

CloudFoundry & $\times$ & $\times$ & $\times$ \\ \hline

OpenShift & \checkmark & $\times$ & $\times$ \\ \hline

AppEngine & \checkmark & $\times$ & $\times$ \\ \hline

Azure & \checkmark & $\times$ & $\times$ \\ \hline

Heroku & \checkmark & $\times$ & $\times$ \\ \hline
\end{tabularx}

\caption{Comparision of cloud providers scaling capabilites}
\label{tab:cloud-providers-scaling}

\end{table}
